The Weakly Nonlinear Saturation of the Magnetorotational Instability

### 2014-10-15 paper/mri_paper.tex
debugging in param space search and paper edits

Equations \ref{momentum} and \ref{induction} are subject to the magnetic solenoid and incompressibility constraints,

@@

>>>>

In the above, the current density $\mathbf{J} = \frac{2}{\beta}\del\times\mathbf{B}$,  Equations \ref{momentum} and \ref{induction} are subject to the magnetic solenoid and incompressibility constraints,

@@

We also define a plasma beta parameter,

\beq
\beta \equiv \frac{\Omega_0^2r_0^2}{v_A^2},
\eeq

where the Alfv\'en sped $v_A$ is

\beq
v_A^2 = \frac{B_0^2}{\rho_0}.
\eeq
